A Survey of Quantitative Descriptions of Molecular Structure

### 2012-04-08 paper.tex
Started on polymer descriptors

@@

Finally, quantum mechanical calculations can also generated
descriptors that can be applied to problems such as QSAR models
(though of course the time complexity of QM derived descriptors do not
make them amenable for large scale virtual screening applications).

>>>>

Finally, quantum mechanical calculations can also generated
descriptors that can be applied to problems such as QSAR models
(though of course the time complexity of QM derived descriptors do not
make them amenable for large scale virtual screening applications).
\textbf{QM descriptors}

\textbf{Descriptors for polymeric systems} Mention the AA suite of
descriptors to characterize things like proteins. Consider related
protein descriptors Mention DNA
descriptors. Mention the polymer descriptors and try and find soem
more.

Polymeric systems represent a challenge for descriptor development. A
number of approaches have been described that includes both
deterministic, geometry derived descriptors \cite{Edvinsson:2003bh} as
well as stochastic methods \cite{Gonzales-Diaz:2003ly}.

@@
